---
title: "jgc2157_hw5"
author: "Gunnar"
date: "11/15/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

libraries
```{r}
library(tidyverse)
library(janitor)
```

Reading homicide csv from github
```{r}
urlfile <- 'https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv'
homicides_df <- read_csv(url(urlfile), na = c(" ", "Unknown"))
```

Creating city_state variable
```{r}
homicides_df <- homicides_df %>%
  mutate(city_state = str_c(city, state, sep = ", "),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved")) %>%
  relocate(city_state) %>%
  filter(city_state != "Tulsa, AL")
```

Filter to Baltimore
```{r}
baltimore_df <- homicides_df %>%
  filter(city_state == "Baltimore, MD")

baltimore_summary <- baltimore_df %>%
  summarise(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test <- prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
)

baltimore_test %>%
  broom::tidy()
```

Table of unsolved and total murders for each city
```{r}
homicides_df %>%
  group_by(city_state) %>%
  summarise(
    unsolved = sum(resolution == "unsolved"),
    n = n()) %>%
  knitr::kable(col.names = c("City", "Unsolved Murders", "Total Murders"))
```

Iterate across cities
First, write a prop.test function and test on a sample city
```{r}
prop_test_function <- function(city_df) {
  
  city_summary <- city_df %>%
  summarise(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

  city_test <- prop.test(
    x = city_summary %>% pull(unsolved),
    n = city_summary %>% pull(n))
  return(city_test)
}

prop_test_function(baltimore_df)
```
Now iterate across all cities

```{r}
results_df <- homicides_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```

Plot of estimates and error bars for each city
```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2
Reading in the data, adding "data/" prefix to files
Then creating nested data for each of the respondents
Seperate particpants by control vs experiment and number
unnest study data and pivot long
```{r}
files_df <- tibble(
  files = list.files("./data")) %>%
  mutate(files = str_c("data", files, sep = "/"))

research_df <- files_df %>%
  mutate(respondents = map(files, read_csv)) %>%
  mutate(study_arm = case_when(str_detect(files, "exp") ~ "experiment",
                               str_detect(files, "con") ~ "control"),
         participant_number = as.factor(parse_number(files))) %>%
  unnest(respondents) %>%
  pivot_longer(cols = week_1:week_8, names_to = "week", values_to = "observations") %>%
  mutate(week = as.numeric(parse_number(week)))
```

Create spaghetti graph of observations over time split by study arm
```{r}
research_df %>%
  ggplot(aes(x = week, y = observations, color = participant_number)) +
  geom_line() +
  ylab("Observations") +
  xlab("Weeks") +
  facet_grid(cols = vars(study_arm)) +
  ggtitle("Observations Over Time by Study Arm")
```

In the above charts showing observations over time stratified by study arm, participants in the control arm appear to report the same observation over time while in the exeriment arm, participants appear to be reporting higher observations as time goes on. 
